On the Dynamics of Anthropomorphism in Robotics \thanks{This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.}

### 2013-05-22 anthropomorphism.tex
Moved paragraph on the limit of our model to the discussion introduction

\section{Initial Model of the Dynamics of Anthropomorphism}
\label{sec:7}

@@

In this section we outline the essence of our initial model of the dynamics of anthropomorphism. This work is still in progress. The ideas we discuss are still incomplete, and their implications for the design of (social) robots and human-robot interaction are still quite speculative. Nonetheless, we believe that even our initial model, incomplete as it is, provides lessons for the understanding and study of anthropomorphism in robotics. However, we view this paper as only setting the stage for further research, realizing full well that it raises many more questions than it answers.

@@

\section{Discussion}
\label{sec:8}

>>>>

\section{A Model of the Dynamics of Anthropomorphism}
\label{sec:dynamics_model}

@@

@@

\section{Discussion}
\label{sec:discussion}

The model of anthropomorphism we propose is still a work in progress. In
particular, its implications regarding the design of (social) robots and
human-robot interaction are still to be refined.

In this section, we discuss more speculative aspects and hypothesis that follow
from the model. These aspects would require further investigation and
experimental support to be validated.
